Proportions of Variants of Concern in NML Wastewater Data

### 2022-05-13 report/ms.tex
Writing progress (and commit test)

These residuals can hold important clues for possible omitted lineages.

>>>>

These residuals can hold important clues for potential misspecification of the variant matrix.
If there are mutations that have high prevalence in the data but low prevalence in the expected counts, this might indicate that it is a representative mutation from a lineage that is not present in the data.
